---
title: "README"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Exploring Election and Census Highly Informative Data Nationally for Indonesia ( Eechidna R package)

The R package *indoelectdata* provides data from Indonesia election. the election data from the 2014 Legislative election including census data from the Indonesian Statistics office, and tweets data from twitter.

## How to install

You can install the latest release of the package from CRAN like this

```{r eval = FALSE}
install.packages("indoelectdata")
```

Or you can install the development version from github, which may have some changes that are not yet on CRAN, using `devtools`, like this:

```{r eval = FALSE}
devtools::install_github("FahroziFahrozi/indoelectdata", 
                         build_vignettes = TRUE)
```

If you are using Linux, you may need some additional libraries for the mapping functions, you can get these with this line:

```
apt-get install libgdal-dev libgeos-dev -y
```
## License

This package is free and open source software, licensed under 
GNU Affero General Public License v3.0

## Feedback, contributing, etc.

Please open an issue if you find something that doesn't work as expected or have questions or suggestions. 
## Acknowledgements 
Thanks to Ben Marwick and Jeremy Forbes for their [cartogram](https://github.com/ropenscilabs/eechidna) package which supplies the examples for this package. 

