---
title: "Sentiment analysis twitter legislative election"
author: "Fahrozi" 
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{exploring-the-census data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)
```

## Exploring the Indonesia census data 2010

This vignette documents used how to explore and see the sentiment analysis about the legislative election in Indonesia, data collected from the twitter tweets and used official twitter APIs.


```{r sentimentanalysis_aboutelection in Indonesia, eval = FALSE}

library(twitteR)
library(RSentiment)
# library(sentiment)
library(tm)
library(NLP)
library(Rstem)
library(plyr)
library(ggplot2)
library(wordcloud)
library(RColorBrewer)

data(some_tweets)
data(sentiment_df)
```

in this part we want to remove the hastag and other twitter handles, because we dont need to use it 

#remove the hastags and other twitter handles
```{r call_dataset_and__removehastags}
some_txt = sapply(some_tweets, function(x) x$getText())
some_txt = gsub("(RT|via)((?:\\b\\W*@\\w+)+)", "", some_txt)
some_txt = gsub("@\\w+", "", some_txt)
some_txt = gsub("[[:punct:]]", "", some_txt)
some_txt = gsub("[[:digit:]]", "", some_txt)
some_txt = gsub("http\\w+", "", some_txt)
some_txt = gsub("[ \t]{2,}", "", some_txt)
some_txt = gsub("^\\s+|\\s+$", "", some_txt)
try.error = function(x)
{
  y = NA
try_error = tryCatch(tolower(x), error=function(e) e)
if (!inherits(try_error, "error"))
y = tolower(x)
return(y) }
some_txt = sapply(some_txt, try.error)
some_txt = some_txt[!is.na(some_txt)]
names(some_txt) = NULL
class_emo = classify_emotion(some_txt, algorithm="bayes", prior=1.0)
emotion = class_emo[,7]
emotion[is.na(emotion)] = "unknown"
class_pol = classify_polarity(emotion, algorithm="bayes")
polarity = class_pol[,4]
```

#contains tweets about the keyword"pemilu legislatif"
```{r collect_thetweetts}
sentiment_df = data.frame(text=some_txt, emotion=emotion,
polarity=polarity, stringsAsFactors=FALSE)
sentiment_df = within(sentiment_df,
emotion <- factor(emotion, levels=names(sort(table(emotion), decreasing=TRUE))))
```

#plot about emotion from the tweets
this part to answer the emotion that we got from the keyword "pemilu legilatif" tweets
```{r plot_thetweets}
ggplot(sentiment_df, aes(x=emotion)) +
geom_bar(aes(y=..count.., fill=emotion)) +
scale_fill_brewer(palette="Dark2") +
labs(x="emotion categories", y="number of tweets") +
labs( "Sentiment Analysis of Tweets about pemilu legislatif\n(classification by emotion)",
plot.title = element_text(size=12))
```

from the result above show that mostly emotions that got from the keyword tweets "pemilu legislative" from the result got that there are unknown and anger emotion.

#polarities from the tweets
this part to answer the polarities from the tweets
```{r sentimentanalysis_polarities}
ggplot(sentiment_df, aes(x=polarity)) +
geom_bar(aes(y=..count.., fill=polarity)) +
scale_fill_brewer(palette="RdGy") +
labs(x="polarity categories", y="number of tweets") +
labs( "Sentiment Analysis of Tweets about pemilu legislatif\n(classification by emotion)",
plot.title = element_text(size=12))
```
from the results we can see that there are 150 positive tweets and others tweets were negative.

#wordscloud
in this part showed the words that mostly people wrote on the twitter about election
```{r wordcloud}
emos = levels(factor(sentiment_df$emotion))
nemo = length(emos)
emo.docs = rep("", nemo)
for (i in 1:nemo)
{
tmp = some_txt[emotion == emos[i]]
emo.docs[i] = paste(tmp, collapse=" ")
}
emo.docs = removeWords(emo.docs, stopwords("english"))
corpus = Corpus(VectorSource(emo.docs))
tdm = TermDocumentMatrix(corpus)
tdm = as.matrix(tdm)
colnames(tdm) = emos
comparison.cloud(tdm, colors = brewer.pal(nemo, "Dark2"),
scale = c(3,.5), random.order = FALSE, title.size = 1.5)
```



